Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-08 paper/ms.tex
many changes
- move review to appendix
- many new refs
- 6Li
- remove krios accretion hypothesis

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\normal}{{\mathcal{N}}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\bs{#1}}
\newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
\newcommand{\msun}{\ensuremath{{\mathrm M}_\odot}}
\newcommand{\pc}{{\rm pc}}
\newcommand{\data}{\mathrm{data}}
\newcommand{\snr}{[S/N]_\varpi}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\absdvtan}{\ensuremath{|\Delta\vec v_\mathrm{t}|}}
\newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  This is the largest and the most significant chemical difference found in
  a wide binary pair yet.
  Additionally, it shows anomalously high surface lithium abundance
  ($A(\elem{Li}=2.75$), higher by $0.5$~dex than its companion.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
  refractory elements in its surface and convective envelope.
\end{abstract}

@@

Binary stars that form from the same birth cloud start with nearly identical
composition.
A differential analaysis of the chemical composition of binary stars can reveal
their history through the chemical signatures related to planet formation or
accretion regardless of the Galactic chemical evolution.
\askjmb{
For example, \citealt{Fischer:2005aa} showed that the higher metallicity in
stars hosting close-in giant planets compared to those without likely promotes
the formation of giant planets by increasing the availability of small particle
condensates that form planetesimals.
}
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

High resolution spectroscopic studies of binary star systems hosting at least
one planet
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
have yielded varied results:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
A possible explanation for the increasing abundance difference with
condensation temperature is that more yet-undiscovered rocky planets formed
around the relatively refractory-poor star
(\citealt{Ramirez:2015aa,Biazzo:2015aa}).
Alternatively, late time accretion of refractory-rich planetary material to the
relatively refractory-rich star can also produce the trend.
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often at $\approx 0.05$~dex level making them challenging to detect even
with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
and differential analyses of two stars that are very similar in their
stellar parameters.

@@

\subsection{
  Review of Detailed Chemical Abundance Studies of Stars in Comoving Pairs}
\label{sub:review}

Anticipating the forthcoming discussion, we review and summarize a handful of
wide binary systems that have been studied in their detailed chemical
abundances so far with high-resolution spectroscopy.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We focus on key characteristics of stars and planets, and interpretations of
any trend in $\Delta\elemH{X}$ with \Tcondens.

\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added}

{\bf 16 Cygni A/B:}
The chemical composition of this well know pair of solar-type stars (G1.5/G3)
has been studied many times.
The hotter star 16 Cyg A has no detected planets, but a M dwarf companion $\sim
70$~AU away in projected separation which is probably physically associated
(\citealt{2002ApJ...581..654P}), and may have affected planet formation process
around the star (\citealt{1996ApJ...458..312J,2005MNRAS.363..641M}).
The other star, 16 Cyg B, hosts a giant planet on an eccentric orbit ($e=0.63$,
\citealt{1997ApJ...483..457C}).
While past measurements of metallicity and abundance difference between the two stars
claimed conflicting results (\citealt{2001ApJ...553..405L,2011ApJ...737L..32S}),
recent studies using high quality spectra consistently reported that
A is more metal rich than B by $\approx 0.04 \pm 0.005$~dex.
However, there is still a disagreement between studies on
whether abundance differences shows a correlation with $\Tcondens$ as well as
its interpretation.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelope of the
host star, they can match the mass difference of gas giant planets around each
star, which is at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
opposite would be true.

{\bf HD~133131A/B:}

@@

The fact that the two stars share nearly identical space motion
at a separation of $< 1$~pc strongly supports that the pair is coeval.
We therefore consider other age indicators apart from their phase-space
coordinates to assess the ages and coevality of the two stars.
First, given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
we can constrain the ages of the two stars by
comparing these values to theoretical isochrones.
We perform isochrone fitting to these values using the Yale-Yonsei model
isochrones (\citealt{2013ApJ...776...87S}).
The input data are $\log(g)$, $T_\mathrm{eff}$, \feh,
parallaxes, $B$-band magnitudes, and their errors.
The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
solar lithium abundance and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
among all measured elements.
This translates to a $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been
attributed to the engulfment of substellar companions such as gas giant planets
or brown dwarfs which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).

In fact, the surface lithium abundance is the only indication that points to
younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
and found no evidence for indications of activity in their spectral energy
distributions.
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential (similar to \texttt{MWPotential2014} from
\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\todo{needs references for vertical action as age indicator}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation.

@@

Although the data described above strongly suggests that the two stars are
coeval, we may still consider scenarios in which the two stars are not actually
born together.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
which is low enough to be negligible.

In fact, any exchange scattering scenario is unsatisfactory as typical
field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
unlikely to show the abundance difference pattern observed.
In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
\bizarreone-\sunanalog\ with the distribution of abundance differences,
$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
\feh\ as \bizarreone\ and \sunanalog.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are typically enhanced at a similar level, with some variations.
Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
unlikely to arise from variations in Galactic chemical evolution.

\todo{HOGG: to provide some theoretical account adding to the above empirical evidence.}

@@

Assuming that the two stars were born together, one possibility to
explain the chemical difference is that there was chemical inhomogeneity within
the birth cloud.
However, there is already ample evidence against such a scenario.
First, none of the other seven similar wide binaries examined in
\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a difference in particular elements as large as
$\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}).
This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
23 wide binaries of late F to K dwarfs, and found most pairs show a difference
in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
binaries have the same chemical composition with $\gtrsim 0.01$~dex
uncertainties.
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
not likely due to chemical inhomogeneity in the birth cloud.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{toycalc.png}
  \caption{
    Comparing the observed abundance difference vs. \Tcondens\ rank
    to the expected change in solar surface abundance after adding $20$~\mearth\ of
    material with bulk Earth composition (\citealt{mcdonough2001composition}).
    The assumed mass fraction in the convective zone is $0.03$.
    All metals are ranked by their \Tcondens\ for solar composition gas,
    and the condensation temperature may be read from the gray line and right y-axis,
    same as in \figname~\ref{fig:relabun_tcrank}.
    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
    indicated by a vertical line and its symbol.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $20$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated with a red arrow
    (see text for details).
  }
  \label{fig:toycalc}
\end{figure}

@@

Another possibility that two coeval stars may end up with different surface
abundances is accretion of planetary material after birth.
Instabilities may develop in a multi-planet system due to its chaotic nature
which may lead to planet engulfment or ejection by the host star
(\todo{needs references}).
%TODO: kozai?
Indeed, it is an important goal of many exoplanet studies
to detect chemical signatures of planet formation or accretion,
distinguish them from Galactic chemical evolution, and
connect them to theories of evolution of planetary systems.
One approach that is free from confusion with Galactic chemical evolution
is to compare two almost identical stars in a wide binary system.
Assuming that the component stars were born together with identical
initial composition, we may see a difference in their surface abundances
if the two stars then accreted different amounts of planetary material.
The resulting abundance difference may depend on the condensation
temperatures of elements in the protoplanetary disks from which the accreted
planets formed, as their compositions depend on the radial temperature gradient
in the disk.
%TODO: cautions on condensation temperature
% 1. it is just a proxy
% 2. it is **equlibrium** condensation temperature

In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
of each element.
The equilibrium condensation temperatures for the composition of solar system
are taken from \citealt{2003ApJ...591.1220L} (Table~8).
The difference seen in \bizarreone-\sunanalog\ is
compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
The metallicity difference of $\approx 0.2$~dex observed in this pair
is larger than the differences seen in any other pairs studied so far.
Strikingly, the five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
strongly suggests that accretion of rocky material has occured in \bizarreone.

@@

We report the discovery of a comoving pair of bright
solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
(\Tcondens)-dependent abundance differences.
The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
The two stars also have anomalously high surface \elem{Li} abundance compared
to their ages of $\sim 4$~Gyr.
We consider that the comoving pair may have formed from two stars of different
birth origins in a exchange scattering event, or that there may be chemical
inhomogeneity in the birth cloud, and find both unlikely.

>>>>

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\normal}{{\mathcal{N}}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\bs{#1}}
\newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
\newcommand{\msun}{\ensuremath{{\mathrm M}_\odot}}
\newcommand{\pc}{{\rm pc}}
\newcommand{\data}{\mathrm{data}}
\newcommand{\snr}{[S/N]_\varpi}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\absdvtan}{\ensuremath{|\Delta\vec v_\mathrm{t}|}}
\newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}
\newcommand{\maccreted}{\ensuremath{15~\mearth}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  % TODO: Hmmm...
  This is the largest and the most significant chemical difference found in
  a wide binary pair yet.
  Additionally, it shows an anomalously high surface lithium abundance
  ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', accreted
  \maccreted\ of rocky material after birth selectively enhancing the
  refractory elements as well as lihtium in its surface and convective
  envelope.
\end{abstract}

@@

Binary stars that form from the same birth cloud start with nearly identical
composition.
A differential analysis of the chemical composition of binary stars can reveal
their history through the chemical signatures related to planet formation or
accretion regardless of the Galactic chemical evolution.
\askjmb{
For example, \citealt{Fischer:2005aa} showed that the higher metallicity in
stars hosting close-in giant planets compared to those without likely promotes
the formation of giant planets by increasing the availability of small particle
condensates that form planetesimals.
}
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state (e.g., \citealt{Pinsonneault:2001aa}).
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

High resolution spectroscopic studies of binary star systems hosting at least
one planet (\citealt{2011ApJ...740...76R,2014ApJ...790L..25T,Teske:2013aa,
  Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab})
have yielded varied results:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
A possible explanation for the difference is that
forming more gas giants or rocky planets leads to
an overall or \Tcondens-dependent depletion
(\citealt{Ramirez:2015aa,Biazzo:2015aa}).
Alternatively, late time accretion of refractory-rich planetary material to the
relatively refractory-rich star can also produce the trend.
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often at $\approx 0.05$~dex level making them challenging to detect even
with a careful analysis of high-resolution, high signal-to-noise ratio spectra,
and differential analyses of two stars that are very similar in their
stellar parameters.
We refer the readers to Appendix~\ref{app:review} for a review of
a handful of individual pairs studied in their detailed chemical abundances
(see also \citealt{2016arXiv161104064M}).

@@

@@

Apart from their closeness in phase-space coordinates,
we can constrain the ages of the two stars
given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$
by comparing these values to theoretical isochrones.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars
(\citealt{2003AJ....126..778V}).
We then combine the luminosities with effective temperature, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star using
a grid of Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval.

{\bf
The surface lithium abundance in a Sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
Thus, surface lithium abundance can be an indicator of stellar ages,
especially whether the star is very young ($\lesssim 1$~Gyr).
The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
Generally, cooler stars with larger convective envelope have lower \elem{Li}
abundance.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
is typical for its \teff.
On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
which has lower \teff\ than \sunanalog, is not only higher than that of
\sunanalog\ but also much higher compared to other field stars of similar \teff.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
red giant stars to the engulfment of substellar companions such as gas giant
planets or brown dwarfs which may replenish $\elem{Li}$.
}

The surface lithium abundance of \bizarreone\ is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then
they may have been part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving
pairs using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
and found no evidence for indications of activity in their spectral energy
distributions.
%
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential (similar to \texttt{MWPotential2014} from
\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\citealt{Wielen:1977,Aumer:2016}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that the unusually high \elem{Li} abundance of
\bizarreone\ requires an alternative explanation.

@@

While the data described above strongly suggests that the two stars are coeval,
this subsection explores the possibility that this pair is not a primordial
binary.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
low enough to be negligible.

An exchange scattering scenario is unlikely to be able to explain
the observed abundance difference pattern of \bizarreone\ and \sunanalog.
We test this by randomly drawing pairs of stars in the sample of
\citealt{2016ApJS..225...32B} from two \feh\ bins at $\feh = 0 \pm 0.025$
and $\feh = 0.2 \pm 0.025$, each similar to \sunanalog\ and \bizarreone.
In \figname~\ref{fig:deltaXH}, we compare the observed abundance difference of
\bizarreone-\sunanalog\ with the distribution of abundance differences
from 300 random pairs.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are typically enhanced at a similar level, with some variations.
Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the low
[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
unlikely to arise from variations in Galactic chemical evolution.

@@

In this subsection, we explore the hypothesis that chemical inhomogeneity
within the birth cloud is the source of the observed abundance difference.
There is ample evidence against this scenario as most wide binaries show in
\feh\ less than $0.02$~dex (\citealt{Desidera:2004aa,Gratton:2001aa}.
In the cases in which a significant difference is detected
with high-precision abundance measurements (see \sectionname~\ref{app:review}),
the difference is typically $\sim 0.05$~dex.
Consistent with these results,
none of the other seven similar wide binaries examined in
\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a difference in particular elements as large as
$\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}, black lines).
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
unlikely to be due to chemical inhomogeneity in the birth cloud.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference (blue circles) to the expected
    change in solar surface abundance after adding \maccreted\ of material
    with bulk Earth composition (\citealt{2003TrGeo...2..547M}; black open and
    filled circles).
    The assumed mass fraction in the convective zone is $0.02$.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas on the $x$-axis.
    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
    in filled circles, while those without a measurement are left open.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $15$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated in the inset.
  }
  \label{fig:toycalc}
\end{figure}

@@

Another possibility that two coeval stars may end up with different surface
abundances is accretion of planetary material after birth.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
Indeed, it is an important goal of many exoplanet studies
to detect chemical signatures of planet formation or accretion,
distinguish them from Galactic chemical evolution, and
connect them to theories of evolution of planetary systems.
One approach that is free from confusion with Galactic chemical evolution
is to compare two almost identical stars in a wide binary system.
Assuming that the component stars were born together with identical
initial composition, we may see a difference in their surface abundances
if the two stars then accreted different amounts of planetary material.
The resulting abundance difference may depend on the condensation
temperatures of elements in the protoplanetary disks from which the accreted
planets formed, as their compositions depend on the radial temperature gradient
in the disk.
%TODO: cautions on condensation temperature
% 1. it is just a proxy
% 2. it is **equlibrium** condensation temperature

In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
of each element.
The equilibrium condensation temperatures for the composition of solar system
are taken from \citealt{2003ApJ...591.1220L} (Table~8).
The difference seen in \bizarreone-\sunanalog\ is
compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
The metallicity difference of $\approx 0.2$~dex observed in this pair
is larger than the differences seen in any other pairs studied so far.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
strongly suggests that accretion of rocky material has occurred in \bizarreone.

@@

We report and discuss the discovery of a comoving pair of bright
solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
(\Tcondens)-dependent abundance differences.
The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
It also has an anomalously high surface \elem{Li} abundance for its age of
$\sim 4$~Gyr, and its effective temperature very close to that of the Sun.
We consider that the comoving pair may have formed from two stars of different
birth origins in a exchange scattering event
(\sectionname~\ref{sub:exchange_scattering}), or that there may be chemical
inhomogeneity in the birth cloud
(\sectionname~\ref{sub:chemical_inhomogeneity_in_star_formation}) to find
both unlikely.
